### 2020-04-06 system-model.tex
:pencil: Fix subchannels

		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{U \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$ respectively. At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$. Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$. Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively. Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$. The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel. Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
		\begin{equation}	\label{eq:h_k}
			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{H}_I} \right)
		\end{equation}
		On top of this, we select the $n$-th of every $N$ entries and combine them to form a subchannel as $\boldsymbol{h}_{k,n}=[h_{k,n,m},\dots,h_{k,n,M}] \in \mathbb{C}^{1 \times M}$ to describe the frequency response at subband $n$ for user $k$, where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}$.
	\end{subsection}

@@

	\begin{subsection}	{Information Decoder}
		In the
	\end{subsection}
\end{section}

>>>>

		Denote the baseband equivalent channels from the AP to user $k$, from the AP to the IRS, and from the IRS to user $k$ as $\boldsymbol{h}_{D,k} \in \mathbb{C}^{1 \times MN}$, $\boldsymbol{H}_I \in \mathbb{C}^{U \times MN}$, and $\boldsymbol{h}_{R,k} \in \mathbb{C}^{1 \times UN}$ respectively. At subband $n$, we collect the frequency response of both direct and reflective links from $M$ and $U$ elements to user $k$ as $\boldsymbol{h}_{D,k,n}=[h_{D,k,n,1},\dots,h_{D,k,n,M}] \in \mathbb{C}^{1 \times M}$ and $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{D,k,n,U}] \in \mathbb{C}^{1 \times U}$. Similarly, the $n$-th incident channel gain matrix from $M$ transmit antennas to $U$ reflectors is expressed as $\boldsymbol{H}_{I,n}=[\boldsymbol{h}_{I,1,n}^T,\dots,\boldsymbol{h}_{I,U,n}^T]^T \in \mathbb{C}^{U \times M}$, with $\boldsymbol{h}_{I,u,n}=[h_{I,u,n,1},\dots,h_{I,u,n,M}] \in \mathbb{C}^{1 \times M}$. We also define the channel between antenna $m$ and all IRS elements as $\boldsymbol{h}_{I,n,m}=[h_{I,1,n,m},\dots,h_{I,U,n,m}]^T$, as represented by the columns of $\boldsymbol{H}_{I,n}$. Element $u$ of the IRS receives a superposed waveform through the multipath channel, then redistribute it by adjusting the reflection coefficient $r_u = \beta_u e^{j \theta_u}$, where $\beta_u \in [0,1]$ and $\theta_u \in [0,2\pi)$ are the amplitude reflection coefficient and phase shift respectively. Each passive reflector harvests a small portion ($1 - \beta_u$) of the signal to support CSI decoding and impedance matching. Construct a diagonal subband-wise IRS matrix by collecting the reflection coefficients of all reflectors onto the diagonal entries such that $\boldsymbol{R}_0 = \text{diag}(r_1, \dots, r_U) \in \mathbb{C}^{U \times U}$. With the assumption of frequency-flat reflection, the IRS matrix is formed by stacking $\boldsymbol{R}_0$ over $N$ subbands such that $\boldsymbol{R} = [\boldsymbol{R}_0^T,\dots,\boldsymbol{R}_0^T]^T \in \mathbb{C}^{UN \times U}$. The IRS-aided extra links can be modeled as a concatenation of the AP-IRS channel to the IRS reflection matrix and the IRS-user channel. Both the direct link and the IRS-aided link contributes to the composite channel $\boldsymbol{h}_k \in \mathbb{C}^{1 \times MN}$ as
		\begin{equation}	\label{eq:h_k}
			\boldsymbol{h}_k = \left( \boldsymbol{h}_{D,k}+\boldsymbol{h}_{R,k} \boldsymbol{R} \boldsymbol{\boldsymbol{H}_I} \right)
		\end{equation}
		On top of this, we select the $n$-th from its every $N$ entries and combine them to form a subchannel $\boldsymbol{h}_{k,n} \in \mathbb{C}^{1 \times M}$ as
		\begin{equation}	\label{eq:h_{k,n}}
			\begin{split}
				\boldsymbol{h}_{k,n}
				&=\boldsymbol{h}_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{H}_{I,n}	\\
				&=[h_{k,n,1},\dots,h_{k,n,M}]
			\end{split}
		\end{equation}
		where $h_{k,n,m}=h_{D,k,n,m}+\boldsymbol{h}_{R,k,n}\boldsymbol{R}_0\boldsymbol{h}_{I,n,m}$.
	\end{subsection}

@@

	\begin{subsection}	{Information Decoder}
		One major benefit of using proposed waveform is that as a translation, the deterministic power term $\boldsymbol{x}_P(t)$ bears no information and creates no interference to the modulated information term $\boldsymbol{x}_I(t)$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}	\label{eq:I_k}
			\begin{split}
				I_k(\boldsymbol{w}_I,\boldsymbol{R},\rho)
				&=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert\boldsymbol{h}_{k,n}\boldsymbol{w}_{I,n}\rvert^2}{\sigma_n^2}\right)}	\\
				&=?
			\end{split}
		\end{equation}

\end{section}
